Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Add a comment
BCP: Spec and library are in separate files now

@@

We present a step-by-step refinement of a library
that contains both implementation and specs.  Each line of code is
only given once when introduced, subsequent code fragments are
incremental updates.  The reader is asked to substitute code parts as
appropriate.

>>>>

\begin{quote}
\begin{itemize}
    \item
        We already added markup support for interactive examples to
        Haddock, back in 2010; and Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.

    \emph{kazu: I guess that it's enough to describe this in the Implementation Section.}
\end{itemize}
\end{quote}

@@

We present a step-by-step refinement of a library
that, and a corresponding spec.  Each line of code is
only given once when introduced, subsequent code fragments are
incremental updates.  The reader is asked to substitute code parts as
appropriate.
